Synthesising rodent trapping studies in West Africa to understand the hazard of zoonotic infectious disease outbreaks.

### 2022-03-09 reports/manuscript_v2.Rmd
updating analysis

---
title: "A scoping review of rodent trapping studies to understand the prevalence of zoonotic disease in West Africa."
date: "`r Sys.Date()`"
author: 
  - "David Simons, Lauren A. Attfield, Kate E. Jones, Deborah Watson-Jones and Richard Kock"
    # url: https://www.dsimons.org
    # orcid_id: 0000-0001-9655-1656
output: 
  # distill::distill_article:
  #   toc: true
  #   toc_depth: 3
  #   toc_float: true
  word_document:
    toc: true
    toc_depth: 3
  # pdf_document:
  #   toc: true
  #   toc_depth: 3
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here())
  })
always_allow_html: yes
bibliography: citations/manuscript_citations.bib
---
```{r, echo=FALSE, include=FALSE}
source(here::here("scripts", "manuscript_library.R"))
```

@@

The potential effect of zoonotic infectious disease outbreaks on human health and societies has been dramatically highlighted by the ongoing SARS-CoV-2 pandemic and recent Ebola virus outbreaks. The number of zoonotic spillover events is projected to increase under intensifying anthropogenic pressure such as; increased human populations [@allen_global_2017], increasing urbanisation [@hassell_urbanization_2017], land use change [@@garcia-pena_land-use_2021] and global climate change [@morse_prediction_2012]. In addition, two taxa - rodents (Rodentia) and bats (Chiroptera) - are proposed to contribute to the greatest number of zoonotic pathogens and the greatest risk of novel pathogen emergence [@han_rodent_2015]. Of 2,220 extant rodent species, 244 (10.7%) are described as being reservoirs of 85 zoonoses [@han_global_2016]. Specifically, West Africa has previously been identified as a region at increased hazard for rodent-borne zoonotic spillover events under different projected scenarios [@garcia-pena_land-use_2021]. Rodents are implicated in the transmission pathways of several human diseases in this region, including, Lassa fever, Schistosomiasis and Leptospirosis [@meerburg_rodent-borne_2009].

>>>>

---
title: "Synthesising rodent trapping studies in West Africa to understand the hazard of zoonotic infectious disease outbreaks."
date: "`r Sys.Date()`"
author: 
  - "David Simons^1, 2, 3^, Lauren A. Attfield, Kate E. Jones, Deborah Watson-Jones and Richard Kock"
    # url: https://www.dsimons.org
    # orcid_id: 0000-0001-9655-1656
output: 
  # distill::distill_article:
  #   toc: true
  #   toc_depth: 3
  #   toc_float: true
  word_document:
    toc: true
    toc_depth: 3
  # pdf_document:
  #   toc: true
  #   toc_depth: 3
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here())
  })
always_allow_html: yes
bibliography: citations/manuscript_citations.bib
---
```{r, echo=FALSE, include=FALSE}
source(here::here("scripts", "manuscript_library.R"))
```

@@

The potential effect of zoonotic infectious disease outbreaks on human health and societies has been dramatically highlighted by the ongoing SARS-CoV-2 pandemic and recent Ebola virus outbreaks. The number of zoonotic spillover events is projected to increase under intensifying anthropogenic pressure such as; increased human populations [@allen_global_2017], increasing urbanisation [@hassell_urbanization_2017], land use change [@garcia-pena_land-use_2021] and global climate change [@morse_prediction_2012]. In addition, two taxa - rodents (Rodentia) and bats (Chiroptera) - are proposed to contribute to the greatest number of zoonotic pathogens and the greatest risk of novel pathogen emergence [@han_rodent_2015]. Of 2,220 extant rodent species, 244 (10.7%) are described as being reservoirs of 85 zoonoses [@han_global_2016]. Specifically, West Africa has previously been identified as a region at increased hazard for rodent-borne zoonotic spillover events under different projected scenarios [@garcia-pena_land-use_2021]. Rodents are implicated in the transmission pathways of several human diseases in this region, including, Lassa fever, Schistosomiasis and Leptospirosis [@meerburg_rodent-borne_2009].
